---
title: "Final_q2"
author: "Amber Duevel"
date: "4/26/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dice}
#rolling the dice and adding it's sum to the players current position
dice_simple<- function(verbose= FALSE){
  face<- sample(1:6, 2, replace=TRUE)
  movement=sum(face)
}
```

```{r board}
#mono_board is a dataframe which holds 40 space objects, with Go being the first space
mono_board = data.frame()
#the 40 space objects as a vector
go = c("Go", 0, 200, 0, "None")
mediterranean = c("Mediterranean Avenue", 0, 172, 0, "Purple")
community1 = c("Community Chest1", 0, 155, 0, "Cards")
baltic = c("Baltic Avenue", 0, 136, 0, "Purple")
income = c("Income Tax", 0, 118, 0, "None")
reading = c("Reading Railroad", 0, 100, 0, "Railroad")
oriental = c("Oriental Avenue", 0, 82, 0, "Light Blue")
chance1 = c("Chance1", 0, 64, 0, "Cards")
vermont = c("Vermont Avenue", 0, 46, 0, "Light Blue")
connecticut = c("Connecticut Avenue", 0, 28, 0, "Light Blue")
just_visiting_jail = c("Just Visiting/Jail", 0, 0, 0, "None")
charles = c("St. Charles Place", 0, 0, 28, "Pink")
electric = c("Electric Company", 0, 0, 46, "Utilities")
states = c("States Avenue", 0, 0, 64, "Pink")
virginia = c("Virginia Avenue", 0, 0, 82, "Pink")
penn_railroad = c("Pennsylvania Railroad", 0, 0, 100, "Railroad")
james = c("St. James Place", 0, 0, 118, "Orange")
community2 = c("Community Chest2", 0, 0, 136, "Cards")
tennessee = c("Tennessee Avenue", 0, 0, 154, "Orange")
new_york = c("New York Avenue", 0, 0, 172, "Orange")
parking = c("Free Parking", 0, 0, 200, "None")
kentucky = c("Kentucky Avenue", 0, 28, 200, "Red")
chance2 = c("Chance2", 0, 46, 200, "Cards")
indiana = c("Indiana Avenue", 0, 64, 200, "Red")
illinois = c("Illinois Avenue", 0, 82, 200, "Red")
b_o = c("B&O Railroad", 0, 100, 200, "Railroad")
atlantic = c("Atlantic Avenue", 0, 118, 200, "Yellow")
ventnor = c("Ventnor Avenue", 0, 136, 200, "Yellow")
water = c("Water Works", 0, 155, 200, "Utilities")
marvin = c("Marvin Gardens", 0, 172, 200, "Yellow")
jail = c("Go to Jail", 0, 200, 200, "None")
pacific = c("Pacific Avenue", 0, 200, 172, "Green")
carolina = c("North Carolina Avenue", 0, 200, 154, "Green")
community3 = c("Community Chest3", 0, 200, 136, "Cards")
penn_avenue = c("Pennsylvania Avenue", 0, 200, 118, "Green")
short = c("Short Line", 0, 200, 100, "Railroad")
chance3 = c("Chance3", 0, 200, 82, "Cards")
park = c("Park Place", 0, 200, 64, "Dark Blue")
luxury = c("Luxury Tax", 0, 200, 46, "None")
boardwalk = c("Boardwalk", 0, 200, 28, "Dark Blue")
#using rbind to add the 40 space objects to mono_board
mono_board = rbind(mono_board, go, mediterranean, community1, baltic, income, reading, oriental, chance1, vermont, connecticut, just_visiting_jail, charles, electric, states, virginia, penn_railroad, james, community2, tennessee, new_york, parking, kentucky, chance2, indiana, illinois, b_o, atlantic, ventnor, water, marvin, jail, pacific, carolina, community3, penn_avenue, short, chance3, park, luxury, boardwalk)
#the column names for mono_board are space_name which holds characters of the name of the space, count which is numeric and holds the number of times the space was landed on in one "game", x-dimension which is numeric and holds the x-coordinate on the graph, y-coordinate which is numeric and holds the y-coordinate on the graph, and space_color which is a character and holds the color of the space or the group that the space belongs best to. 
colnames(mono_board) = c('space_name', 'count', 'x_dimension', 'y_dimension', 'space_color')
#using transform() to have the x-dimension, y-dimension, and count columns be numeric instead of character
mono_board = transform(mono_board, x_dimension = as.numeric(x_dimension))
mono_board = transform(mono_board, y_dimension = as.numeric(y_dimension))
mono_board = transform(mono_board, count = as.numeric(count))
```

```{r turn}
#player_df dataframe which is storing position and money data for each player
player_df = data.frame()
#four players were created with position = 1 and starting money is 1500
player1 = c("player1", 1, 1500)
player2 = c("player2", 1, 1500)
player3 = c("player3", 1, 1500)
player4 = c("player4", 1, 1500)
#using rbind function to add the four player objects to the player_df dataframe
player_df = rbind(player_df, player1, player2, player3, player4)
#the columns in the player_df dataframe are name, position, and money
colnames(player_df) = c("name", "position", "money")
#used transform() to have the position be numeric instead of a character
player_df = transform(player_df, position = as.numeric(position))
num_players = nrow(player_df)
#mono_graph_data is a dataframe which stores the history of each players moves around the board
mono_graph_data = data.frame()
mono_graph_data = rbind(c(player_df[1, 1], mono_board[player_df[1, 2], 3], mono_board[player_df[1, 2], 4]), 
                        c(player_df[2, 1], mono_board[player_df[2, 2], 3], mono_board[player_df[2, 2], 4]), 
                        c(player_df[3, 1], mono_board[player_df[3, 2], 3], mono_board[player_df[3, 2], 4]), 
                        c(player_df[4, 1], mono_board[player_df[4, 2], 3], mono_board[player_df[4, 2], 4]))
#the mono_graph_data dataframe stores the player, x-coordinate on the board plot, and y-coordinate on the board plot, which are each a column
colnames(mono_graph_data) = c('player', 'x_coordinate', 'y_coordinate')
#initially set rounds and current player to 0
rounds = 0
player = 0
#move function which stores roll from dice_simple output and add roll to the current position in player_df and stores in space, and space is returned
move = function() {
  roll = dice_simple()
  space = player_df[player+1, 2] + roll
  #this if else is making sure that space doesn't exceed 40 because the spaces on the board are from 1-40
  if (space == 40) {
    space = 40
  }
  else {
    space = space%%40
  }
  return(space)
}
#player_turn takes in the current player, calls the move function and stores the current space in s, then increases the count on that space by 1 and updates player_df to be the new current space
player_turn = function(player) {
  s = move()
  mono_board[s, 2] = as.numeric(mono_board[s, 2] + 1)
  player_df[player+1, 2] = s
  
  #mono_graph_data is adding a new row to the dataframe with the player name, their x-coordinate, and y-coordinate
  mono_graph_data = rbind(mono_graph_data, c(player_df[player+1, 1], mono_board[player_df[player+1, 2], 3], mono_board[player_df[player+1, 2], 4]))
  
  #need to return the assign mono_board, player_df, and mono_graph_data so that the new dataframes can be stored and called from the global environment
  return(c(assign("mono_board", mono_board, .GlobalEnv), assign("player_df", player_df, .GlobalEnv), assign("mono_graph_data", mono_graph_data, .GlobalEnv)))
}
#running 50 rounds of the game
while (rounds < 100) {
  player_turn(player)
  player = (player+1)%%num_players
  rounds = rounds + 1
}
```

```{r image}
library(grid)
library(jpeg)
library(tidyverse)
library(ggplot2)
library(gganimate)
Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2)
#storing the monopoly board image, monopolyboard.jpg, in board_img
board_img = rasterGrob(readJPEG("monopolyboard.jpg"), 
                       width = unit(1, "npc"), height = unit(1, "npc"))
```

```{r plot}
#using the transform() function to change the x and y-coordinate columns to numeric in mono_graph_data

mono_graph_data = transform(mono_graph_data, x_coordinate = as.numeric(x_coordinate))
mono_graph_data = transform(mono_graph_data, y_coordinate = as.numeric(y_coordinate))

#mono_graph is a scatterplot with the monopoly board as the background and the points are the plots where the players have been. There are four different colors, which represent each player
mono_graph = ggplot(mono_graph_data, group = "player") +
  annotation_custom(board_img) +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 200)) +
  scale_y_continuous(limits = c(0, 200)) +
  geom_point(aes(x = x_coordinate, y = y_coordinate, color = player, size = 5))
mono_graph
```
```{r count}
#count_plot is a bar graph with the space name as the y-axis and count for each space as the x-axis. Colors are grouped based on the type of space and color associated with each space on the board, if any
count_plot = ggplot(mono_board, aes(x = space_name, y = count), group = "space_color") +
  geom_bar(stat = "identity", aes(fill = space_color)) +
  coord_flip() +
  ggtitle("Count for Each Space") +
  ylab("Count") +
  xlab("Space Name") +
  labs(fill = "Type of Space")
count_plot
```
Each spot has an equal probability of being landed on. Due to the fact that we are not checking for doubles, using the cards or having a jail function, all spots have an equal chance. This part of monopoly is simple because it's just relying on the chances of a dice. It's all dictated on the probability of a number on the dice being rolled. A dice has an even probability of each number being landed on so each space should be somewhat equal by the end of the game. We ran our program for one hundred rounds because there isn't a natural stop to the game when you don't deal with money or property. When we did this we got income tax to be landed on the most frequently. If we ran the program for more rounds we would find that each space was landed on an equal amount
