---
title: "STAT 345 Final"
author: "Amber Duevel"
date: "4/19/2022"
output: html_document
---
Rule:
1. Each player starts out with $1,500
2. Each player rolls the dice, the highest roller starts first
3. If you roll doubles three times, move your player to the jail space
4. A player can get out of jail if they roll doubles, use "Get out of jail free card", or pay a fine of $50
5. Everytime a player passes GO they receive $200

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dice}
dice<-function(verbose=FALSE){
  face <- sample(1:6, 2, replace=TRUE)
  if(face[1]==face[2]){
    double = TRUE
    return("Rolled:", face[1], face[2])
    else
    double=FALSE
    movement = sum(face)
    return("Rolled:", face[1], face[2], "Move ", movement, " spaces")
    
  }
}

dice_simple<- function(verbose= FALSE){
  face<- sample(1:6, 2, replace=TRUE)
  movement=sum(face)
}
```

### Actions and Attributes for each Space
This is what will go in the vector for each space:
- name of space
- is property (true/false)
- price of property (could be NA)
- color of space (could be NA)
- pay or gain money (based on positive or negative number). Should I leave as 0 otherwise? Yes, let's do that
- go to jail (true/false)
- free parking (true/false)
- land on go (true/false)
- number of times it is landed on
- x dimension on board
- y dimension on board

```{r board}
mono_board = data.frame()
# All of the spaces on the board
go = c("Go", FALSE, NA, NA, 200, FALSE, FALSE, TRUE, 0, 200, 0)
mediterranean = c("Mediterranean Avenue", TRUE, 60, "Purple", 0, FALSE, FALSE, FALSE, 0, 172, 0)
community1 = c("Community Chest", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 155, 0)
baltic = c("Baltic Avenue", TRUE, 60, "Purple", 0, FALSE, FALSE, FALSE, 0, 136, 0)
income = c("Income Tax", FALSE, NA, NA, -200, FALSE, FALSE, FALSE, 0, 118, 0)
reading = c("Reading Railroad", TRUE, 200, "Railroad", 0, FALSE, FALSE, FALSE, 0, 100, 0)
oriental = c("Oriental Avenue", TRUE, 100, "Light Blue", 0, FALSE, FALSE, FALSE, 0, 82, 0)
chance1 = c("Chance", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 64, 0)
vermont = c("Vermont Avenue", TRUE, 100, "Light Blue", 0, FALSE, FALSE, FALSE, 0, 46, 0)
connecticut = c("Connecticut Avenue", TRUE, 120, "Light Blue", 0, FALSE, FALSE, FALSE, 0, 28, 0)
just_visiting_jail = c("Just Visiting", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 0, 0) # Shares the same space as jail; need to incorporate that somehow. 
charles = c("St. Charles Place", TRUE, 140, "Pink", 0, FALSE, FALSE, FALSE, 0, 0, 28)
electric = c("Electric Company", TRUE, 150, "Utilities", 0, FALSE, FALSE, FALSE, 0, 0, 46)
states = c("States Avenue", TRUE, 140, "Pink", 0, FALSE, FALSE, FALSE, 0, 0, 64)
virginia = c("Virginia Avenue", TRUE, 160, "Pink", 0, FALSE, FALSE, FALSE, 0, 0, 82)
penn_railroad = c("Pennsylvania Railroad", TRUE, 200, "Railroad", 0, FALSE, FALSE, FALSE, 0, 0, 100)
james = c("St. James Place", TRUE, 180, "Orange", 0, FALSE, FALSE, FALSE, 0, 0, 118)
community2 = c("Community Chest", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 0, 136)
tennessee = c("Tennessee Avenue", TRUE, 180, "Orange", 0, FALSE, FALSE, FALSE, 0, 0, 154)
new_york = c("New York Avenue", TRUE, 200, "Orange", 0, FALSE, FALSE, FALSE, 0, 0, 172)
parking = c("Free Parking", FALSE, NA, NA, 10000, FALSE, TRUE, FALSE, 0, 0, 200)
kentucky = c("Kentucky Avenue", TRUE, 220, "Red", 0, FALSE, FALSE, FALSE, 0, 28, 200)
chance2 = c("Chance", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 46, 200)
indiana = c("Indiana Avenue", TRUE, 220, "Red", 0, FALSE, FALSE, FALSE, 0, 64, 200)
illinois = c("Illinois Avenue", TRUE, 240, "Red", 0, FALSE, FALSE, FALSE, 0, 82, 200)
b_o = c("B&O Railroad", TRUE, 200, "Railroad", 0, FALSE, FALSE, FALSE, 0, 100, 200)
atlantic = c("Atlantic Avenue", TRUE, 260, "Yellow", 0, FALSE, FALSE, FALSE, 0, 118, 200)
ventnor = c("Ventnor Avenue", TRUE, 260, "Yellow", 0, FALSE, FALSE, FALSE, 0, 136, 200)
water = c("Water Works", TRUE, 150, "Utilities", 0, FALSE, FALSE, FALSE, 0, 155, 200)
marvin = c("Marvin Gardens", TRUE, 280, "Yellow", 0, FALSE, FALSE, FALSE, 0, 172, 200)
jail = c("Go to Jail", FALSE, NA, NA, 0, TRUE, FALSE, FALSE, 0, 200, 200)
pacific = c("Pacific Avenue", TRUE, 300, "Green", 0, FALSE, FALSE, FALSE, 0, 200, 172)
carolina = c("North Carolina Avenue", TRUE, 300, "Green", 0, FALSE, FALSE, FALSE, 0, 200, 154)
community3 = c("Community Chest", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 200, 136)
penn_avenue = c("Pennsylvania Avenue", TRUE, 320, "Green", 0, FALSE, FALSE, FALSE, 0, 200, 118)
short = c("Short Line", TRUE, 200, "Railroad", 0, FALSE, FALSE, FALSE, 0, 200, 100)
chance3 = c("Chance", FALSE, NA, NA, 0, FALSE, FALSE, FALSE, 0, 200, 82)
park = c("Park Place", TRUE, 350, "Dark Blue", 0, FALSE, FALSE, FALSE, 0, 200, 64)
luxury = c("Luxury Tax", FALSE, NA, NA, -75, FALSE, FALSE, FALSE, 0, 200, 46)
boardwalk = c("Boardwalk", TRUE, 400, "Dark Blue", 0, FALSE, FALSE, FALSE, 0, 200, 28)

mono_board = rbind(mono_board, go, mediterranean, community1, baltic, income, reading, oriental, chance1, vermont, connecticut, just_visiting_jail, charles, electric, states, virginia, penn_railroad, james, community2, tennessee, new_york, parking, kentucky, chance2, indiana, illinois, b_o, atlantic, ventnor, water, marvin, jail, pacific, carolina, community3, penn_avenue, short, chance3, park, luxury, boardwalk)

colnames(mono_board) = c('space_name', 'is_property', 'price_of_property', 'color_of_space', 'pay_gain_money', 'go_to_jail', 'free_parking', 'land_on_go', 'count', 'x_dimension', 'y_dimension')

```

```{r type}
mono_board = transform(mono_board, x_dimension = as.numeric(x_dimension))
mono_board = transform(mono_board, y_dimension = as.numeric(y_dimension))
mono_board = transform(mono_board, count = as.numeric(count))
mono_board = transform(mono_board, price_of_property = as.numeric(price_of_property))

mono_board
```

### Monopoly Board Image

```{r image}
library(grid)
library(jpeg)
library(tidyverse)
library(ggplot2)
library(gganimate)
Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2)

board_img = rasterGrob(readJPEG("monopolyboard.jpg"), 
                       width = unit(1, "npc"), height = unit(1, "npc"))
```


```{r plot}
mono_graph = ggplot(mono_board) +
  annotation_custom(board_img) +
  theme(aspect.ratio = 1) +
  xlim(0, 200) +
  ylim(0, 200) +
  geom_point(aes(x = x_dimension, y = y_dimension))
mono_graph
```

### Community Chest Cards
Attributes for the community chest cards:
- Description of the card
- Gain or lose money(represented by a numeric value, positive or negative or zero). Some may or may not collect money, so we need to create a function for that. Leaving as 0 for now.
- does it move the player?(true/false)
- where does the player move to? Space name (could be NA)

```{r community chest}
cc_cards = data.frame()

cc1 = c("Advance to Go(collect $200)", 200, TRUE, "Go")
cc2 = c("Bank error in your favor. Collect $200", 200, FALSE, NA)
cc3 = c("Doctor's fee. Pay $50", -50, FALSE, NA)
cc4 = c("From sale of stock you get $50", 50, FALSE, NA)
cc5 = c("Get out of jail free", 0, FALSE, NA)
cc6 = c("Go to jail. Go directly to jail, do not pass Go, do not collect $200", 0, TRUE, "Jail")
cc7 = c("Holiday fund matures. Receive $100", 100, FALSE, NA)
cc8 = c("Income tax refund. Collect $20", 20, FALSE, NA)
cc9 = c("It is your birthday. Collect $10 from every player", 0, FALSE, NA)
cc10 = c("Life insurance matures. Collect $100", 100, FALSE, NA)
cc11 = c("Pay hospital fees of $100", -100, FALSE, NA)
cc12 = c("Pay school fees of $50", -50, FALSE, NA)
cc13 = c("Receive $25 consultancy fee", -25, FALSE, NA)
cc14 = c("You are assessed for street repair. $40 per house. $115 per hotel", 0, FALSE, NA)
cc15 = c("You have won second prize in a beauty contest. Collect $10", 10, FALSE, NA)
cc16 = c("You inherit $100", 100, FALSE, NA)

cc_cards = rbind(cc_cards, cc1, cc2, cc3, cc4, cc5, cc6, cc7, cc8, cc9, cc10, cc11, cc12, cc13, cc14, cc15, cc16)

colnames(cc_cards) = c("Card Description")
```

### Chance cards
Attributes for the chance cards:
- Description of the card
- Gain or lose money(represented by a numeric value, positive or negative or zero). Some may or may not collect money, so we need to create a function for that. Leaving as 0 for now.
- does it move the player?(true/false)
- where does the player move to? Space name (could be NA)

```{r chance}
chance_cards = data.frame()

c1 = c("Advance to Boardwalk", 0, TRUE, "Boardwalk")
c2 = c("Advance to Go(collect $200)", 200, TRUE, "Go")
c3 = c("Advance to Illinois Avenue. If you pass Go, collect $200", 0, TRUE, "Illinois Avenue")
c4 = c("Advance to St. Charles Place. If you pass Go, collect $200", 0, TRUE, "St. Charles Place")
c5 = c("Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", 0, TRUE, "Railroad") #Needs to look for the nearest railroad, which it's not doing right now
c6 = c("Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", 0, TRUE, "Railroad") #Same as the previous one
c7 = c("Advance token to the nearest Utility. If unowned, you may buy it from the Bank. If owned, throw dice and pay owner a total ten times amount thrown.", 0, TRUE, "Utility") #Same as the previous one but with utilities
c8 = c("Bank pays you dividend of $50", 50, FALSE, NA)
c9 = c("Get out of jail free", 0, FALSE, NA)
c10 = c("Go back 3 spaces", 0, TRUE, "Current space minus 3")
c11 = c("Go to jail. Go directly to jail, do not pass Go, do not collect $200", 0, TRUE, "Jail")
c12 = c("Make general repairs on all your property. For each house pay $25. For each hotel pay $100", 0, FALSE, NA)
c13 = c("Speeding fine $15", -15, FALSE, NA)
c14 = c("Take a trip to Reading Railroad. If you pass Go, collect $200", 0, TRUE, "Go")
c15 = c("You have been elected Chairman of the Board. Pay each player $50", -50, FALSE, NA)
c16 = c("Your building loan matures. Collect $150", 150, FALSE, NA)

chance_cards = rbind(chance_cards, c1, c2, c3, c4, c5, c6, c7, c8, c9, c10, c11, c12, c13, c14, c15, c16)

colnames(chance_cards) = c("Card Description")
```
## Structure for the Game

### For the Basic Game (with no additional rules)

1. All players start on Go (the first row in the mono_board dataframe)
2. Each player takes their turn, one at a time. For their turn, they follow these steps. These steps will be in one function. 
  - roll the dice
  - the player will move their current space on the board by the number that the dice show. The player object needs to keep track of the space they are currently on. The player object should store this as an integer. In this step, they will update the current space. 
  - increase the count of that space by 1
  - current players turn is over. Next players turn.


```{r turn}
player_turn = function(player) {
  # roll dice and store number in a variable
  
  # take the number from the dice and add that to the current space. Store the new space integer in the same variable
  
}

### Player Objects

library(dplyr)

## players object

players <- setRefClass("player",
                       fields = list(pos="numeric",verbose='logical'),
                       methods = list(
                         move_x = function(x){Space <- if(x == move, current space plus roll, x)Space},
                         go_to_space_x = function(x){Space <- if else(x == go to space, new space, x)Space},
                         trap = function(x){Space <- if else(x == jail space, jail space, x)Space},
                         getout = function(x){Space <- if else(x == get out of jail space, after jail space, x)Space},
                         gotojail = function(x){Space <- if else(x == go to jail space, jail space, x)Space})
                       )

## test for how many times a player can land on a certain part of the board

testing <- setRefClass("testing",
                       fields = list(count = "numeric"),
                       methods = list(increaseby = function(x){count[x] <<- count[x] + 1})
                       )

## main program

## new players

player1 <- players$new(pos = 1, verbose = FALSE)

player2 <- players$new(pos = 1, verbose = FALSE)
```
### Table for money
-money_amount = starting value at the beginning of the game
-property_amount = subtracting when buying a property
-bank_amount = subtracting amount you owe the bank (pay jail, parking ticket, chance card, etc.)
-player_amount = subtracting when you land on another player's property
-reward = adding amount of a reward (if a card says you won a reward etc.)

```{r Money}

money_amount <-150
 
money_board<-function(mono_board){
  if(mono_board[,2]==TRUE){
    money_amount = money_amount - mono_board[3]
    return(money_amount)
  }else{
    return(money_amount)
  }
  if(mono_board[,5]== -200){
    money_amount = money_amount - 200
    return(money_amount)
  }else if(mono_board[,5]== 10000){
    money_amount = money_amount + 10000
    return(money_amount)
  }else if(mono_board[,5]==-75){
    money_amount = money_amount - 75
    return(money_amount)
  }else if(mono_board[,5] == 0){
    return(money_amount)
  }
  if(pos==Go){
    money_amount = money_amount + 200
    return(money_amount)
  }else{
    return(money_amount)
  }
}

money_chance <-function(chance_cards){
  if(chance_cards[,2]==0){
    return(money_amount)
  }else if(chance_cards[,2]==200){
    money_amount = money_amount + 200
    return(money_amount)
  }else if(chance_cards[,2]==50){
    money_amount = money_amount + 50
    return(money_amount)
  }else if(money_amount[,2]==-15){
    money_amount = money_amount - 15
    return(money_amount)
  }else if(money_amount[,2]==-50){
    money_amount = money_amount - 50
    return(money_amount)
  }else if(money_amount[,2]==150){
    money_amount = money_amount + 150
    return(money_amount)
  }
}

money_cc <- function(cc_cards){
  if(cc_cards[,2]==0){
    return(money_amount)
  }else if(cc_cards[,2]==200){
    money_amount = money_amount + 200
    return(money_amount)
  }else if(cc_cards[,2]==-50){
    money_amount = money_amount - 50
    return(money_amount)
  }else if(cc_cards[,2]==50){
    money_amount = money_amount + 50
    return(money_amount)
  }else if(cc_cards[,2]==100){
    money_amount = money_amount + 100
    return(money_amount)
  }else if(cc_cards[,2]==20){
    money_amount = money_amount + 20
    return(money_amount)
  }else if(cc_cards[,2]==-100){
    money_amount = money_amount - 100
    return(money_amount)
  }else if(cc_cards[,2]==-25){
    money_amount = money_amount - 25
    return(money_amount)
  }else if(cc_cards[,2]==10){
    money_amount = money_amount + 10
    return(money_amount)
  }
}
```
