---
title: "Final_q3"
author: "Amber Duevel"
date: "4/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dice}
#checking to see if the dice roll is a double
check_double<-function(face, double_count){
  #does each separate roll match the other
  if(face[1]==face[2]){
    #increasing the count by 1 if it is a double
    double_count=double_count+1
    #if you roll three doubles in a row, the player is sent to jail
    if(double_count==3){
      #11 is position of jail
      player_df[player+1, 2] = 11
      assign("player_df",player_df,.GlobalEnv)
      return(sum(face))
    }
    else {
      #space is the new current space, and updating player_df with the new position, mono_board count increases by 1, and mono_graph_data adds a row with the new data
      space = player_df[player+1, 2] + sum(face)
      if (space == 40) {
        space = 40
      }
      else {
        space = space%%40
      }
    
      mono_board[space, 2] = as.numeric(mono_board[space, 2] + 1)
      player_df[player+1, 2] = space
  
      mono_graph_data = rbind(mono_graph_data, c(player_df[player+1, 1], mono_board[player_df[player+1, 2], 3], mono_board[player_df[player+1, 2], 4]))
      
      #rolls the dice and gets new face value and calls check_doubles, which is a recursive call
      face = sample(1:6,2,replace=TRUE)
      check_double(face, double_count)
    }
  }else{
    #return the sum of the faces and go back to dice function
    assign("mono_board", mono_board, .GlobalEnv)
    assign("player_df", player_df, .GlobalEnv)
    assign("mono_graph_data", mono_graph_data, .GlobalEnv)
    return(sum(face))
  }
}

#calling jail out when a player is in jail and is trying to get out of jail by rolling doubles
jail_out<-function(face, jail_count){
  if(face[1]==face[2]){
    movement=sum(face)
  }else{
    jail_count=jail_count+1
    #by the third round, if you don't roll doubles, player still leaves jail
    if(jail_count==3){
      movement=sum(face)
    }
    return(jail_count)
  }
}

#calling dice with each turn for each player
dice <- function(){
  double_count = 0
  jail_count = 0
  #rolling the dice
  face = sample(1:6,2,replace=TRUE)
  #if the person is in jail we called the jail_out function
  if(player_df[player+1, 2] == 11){
    while(jail_count<3){
      jail_out(face, jail_count)
      break
    }
  }
  #returning the sum of the roll so we can add it to the position
  sum_face = check_double(face, double_count)
  print(sum_face)
  return(sum_face)
}
```

```{r board}
#establishing the monopoly board with positions
mono_board = data.frame()
# All of the spaces on the board
go = c("Go", 0, 200, 0, "None")
mediterranean = c("Mediterranean Avenue", 0, 172, 0, "Purple")
community1 = c("Community Chest1", 0, 155, 0, "Cards")
baltic = c("Baltic Avenue", 0, 136, 0, "Purple")
income = c("Income Tax", 0, 118, 0, "None")
reading = c("Reading Railroad", 0, 100, 0, "Railroad")
oriental = c("Oriental Avenue", 0, 82, 0, "Light Blue")
chance1 = c("Chance1", 0, 64, 0, "Cards")
vermont = c("Vermont Avenue", 0, 46, 0, "Light Blue")
connecticut = c("Connecticut Avenue", 0, 28, 0, "Light Blue")
just_visiting_jail = c("Just Visiting/Jail", 0, 0, 0, "None")
charles = c("St. Charles Place", 0, 0, 28, "Pink")
electric = c("Electric Company", 0, 0, 46, "Utilities")
states = c("States Avenue", 0, 0, 64, "Pink")
virginia = c("Virginia Avenue", 0, 0, 82, "Pink")
penn_railroad = c("Pennsylvania Railroad", 0, 0, 100, "Railroad")
james = c("St. James Place", 0, 0, 118, "Orange")
community2 = c("Community Chest2", 0, 0, 136, "Cards")
tennessee = c("Tennessee Avenue", 0, 0, 154, "Orange")
new_york = c("New York Avenue", 0, 0, 172, "Orange")
parking = c("Free Parking", 0, 0, 200, "None")
kentucky = c("Kentucky Avenue", 0, 28, 200, "Red")
chance2 = c("Chance2", 0, 46, 200, "Cards")
indiana = c("Indiana Avenue", 0, 64, 200, "Red")
illinois = c("Illinois Avenue", 0, 82, 200, "Red")
b_o = c("B&O Railroad", 0, 100, 200, "Railroad")
atlantic = c("Atlantic Avenue", 0, 118, 200, "Yellow")
ventnor = c("Ventnor Avenue", 0, 136, 200, "Yellow")
water = c("Water Works", 0, 155, 200, "Utilities")
marvin = c("Marvin Gardens", 0, 172, 200, "Yellow")
jail = c("Go to Jail", 0, 200, 200, "None")
pacific = c("Pacific Avenue", 0, 200, 172, "Green")
carolina = c("North Carolina Avenue", 0, 200, 154, "Green")
community3 = c("Community Chest3", 0, 200, 136, "Cards")
penn_avenue = c("Pennsylvania Avenue", 0, 200, 118, "Green")
short = c("Short Line", 0, 200, 100, "Railroad")
chance3 = c("Chance3", 0, 200, 82, "Cards")
park = c("Park Place", 0, 200, 64, "Dark Blue")
luxury = c("Luxury Tax", 0, 200, 46, "None")
boardwalk = c("Boardwalk", 0, 200, 28, "Dark Blue")
mono_board = rbind(mono_board, go, mediterranean, community1, baltic, income, reading, oriental, chance1, vermont, connecticut, just_visiting_jail, charles, electric, states, virginia, penn_railroad, james, community2, tennessee, new_york, parking, kentucky, chance2, indiana, illinois, b_o, atlantic, ventnor, water, marvin, jail, pacific, carolina, community3, penn_avenue, short, chance3, park, luxury, boardwalk)
colnames(mono_board) = c('space_name', 'count', 'x_dimension', 'y_dimension', 'space_color')
```

```{r}
#making it so we can display the board as a graph
mono_board = transform(mono_board, x_dimension = as.numeric(x_dimension))
mono_board = transform(mono_board, y_dimension = as.numeric(y_dimension))
mono_board = transform(mono_board, count = as.numeric(count))
```

```{r turn}
#establishing the players and putting them into a data frame
#each player holds what number player, position, and how much money they have
player_df = data.frame()
player1 = c("player1", 1, 1500)
player2 = c("player2", 1, 1500)
player3 = c("player3", 1, 1500)
player4 = c("player4", 1, 1500)
player_df = rbind(player_df, player1, player2, player3, player4)
colnames(player_df) = c("name", "position", "money")
player_df = transform(player_df, position = as.numeric(position))
num_players = nrow(player_df)

#mono_graph_data is a dataframe which stores the history of each players moves around the board
mono_graph_data = data.frame()
mono_graph_data = rbind(c(player_df[1, 1], mono_board[player_df[1, 2], 3], mono_board[player_df[1, 2], 4]), 
                        c(player_df[2, 1], mono_board[player_df[2, 2], 3], mono_board[player_df[2, 2], 4]), 
                        c(player_df[3, 1], mono_board[player_df[3, 2], 3], mono_board[player_df[3, 2], 4]), 
                        c(player_df[4, 1], mono_board[player_df[4, 2], 3], mono_board[player_df[4, 2], 4]))
colnames(mono_graph_data) = c('player', 'x_coordinate', 'y_coordinate')

rounds = 0
player = 0

#moving the players to new positions based on the number they rolled
move = function() {
  roll = dice()
  #adding their roll to their current position
  space = player_df[player+1, 2] + roll
  if (space == 40) {
    space = 40
  }
  else {
    space = space%%40
  }
  return(space)
}
#uses the returned space value and assigns it to s
player_turn = function(player) {
  s = move()
  mono_board[s, 2] = as.numeric(mono_board[s, 2] + 1)
  player_df[player+1, 2] = s
  
  mono_graph_data = rbind(mono_graph_data, c(player_df[player+1, 1], mono_board[player_df[player+1, 2], 3], mono_board[player_df[player+1, 2], 4]))
  
  return(c(assign("mono_board", mono_board, .GlobalEnv), assign("player_df", player_df, .GlobalEnv), assign("mono_graph_data", mono_graph_data, .GlobalEnv)))
}

#number of rounds that the game is played
while (rounds < 40) {
  player_turn(player)
  player = (player+1)%%num_players
  rounds = rounds + 1
}
```

```{r image}
#putting the image of the monopoly board on the graph
library(grid)
library(jpeg)
library(tidyverse)
library(ggplot2)
library(gganimate)
Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2)
board_img = rasterGrob(readJPEG("monopolyboard.jpg"), 
                       width = unit(1, "npc"), height = unit(1, "npc"))
```

```{r plot}
#plotting all the positions that the players are at on the graph
mono_graph_data = transform(mono_graph_data, x_coordinate = as.numeric(x_coordinate))
mono_graph_data = transform(mono_graph_data, y_coordinate = as.numeric(y_coordinate))
mono_graph = ggplot(mono_graph_data, group = "player") +
  annotation_custom(board_img) +
  theme(aspect.ratio = 1) +
  scale_x_continuous(limits = c(0, 200)) +
  scale_y_continuous(limits = c(0, 200)) +
  geom_point(aes(x = x_coordinate, y = y_coordinate, color = player, size = 5))
mono_graph
```

```{r count}
#creating a bar graph of the amount of times each spot on the board is landed on
count_plot = ggplot(mono_board, aes(x = space_name, y = count), group = "space_color") +
  geom_bar(stat = "identity", aes(fill = space_color)) +
  coord_flip() +
  ggtitle("Count for Each Space") +
  ylab("Count") +
  xlab("Space Name") +
  labs(fill = "Type of Space")
count_plot
```
The outcome of this question is very similar to the first question due to the face that we aren't adding cards or the jail function. In this question we are taking into account the double rule. If a player roles a double they can roll again but if a player roles three doubles in a row they are sent to jail. This could impact the space jail. Rolling doubles three times in a row is very unlikely but possible. So we suspect on jail spot to have a higher count than other spaces because it's the only position a player can move to. The other spots are still equally likely to occur.
